Parsing Tweets into Universal Dependencies

### 2017-07-28 paper.tex
twitter specific statistics table

%%%%%%%
\usepackage{graphicx}
\newcommand{\heart}{\ensuremath\heartsuit}

@@

\section{Introduction}
Analyzing the syntax of tweets is challenging for traditional NLP tools because most of the tweet texts are informal and noisy.

@@

\subsection{Linguistic Phenomena of Twitter} \label{introduction}
%Eisenstan
As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into token level and structure level phenomena, and we will discuss them separately.

@@

Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
The development set contains 210 tweets of Tweebank V1 Dev and another 500 tweets in feb\_jul\_16 corpus.
The test set contains all the 201 tweets in the test set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.

@@

% tweets, tokens, tokens/tweet, part/tweet, token types.
\begin{table}[h!]
\centering
 \begin{tabular}{l r r r} 
 \hline
 			& 	Train 		& 	Test		&	Dev\\[0.5ex] \hline
tweets 		&	1639 		&	1201		&	709\\
tokens 		&			&			&	\\
types 		&	 		&			&	\\
utterances 	&	 		&			&	\\ \hline
\end{tabular}
 \caption{Statistics of Tweebank}
 \label{tab1}
\end{table}

% tokens and its proportions for the previous language phenomena.

%annotation statistics, agreement

>>>>

%%%%%%%
\usepackage{graphicx}
\newcommand{\heart}{\ensuremath\heartsuit}
\usepackage{multirow}

@@

\section{introduction}
Analyzing the syntax of tweets is challenging for traditional NLP tools because most of the tweet texts are informal and noisy.

@@

\subsection{Linguistic Phenomena of Twitter} \label{lingphen}
%Eisenstan
As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into token level and structure level phenomena, and we will discuss them separately.

@@

\subsubsection{Basic Statistics}
Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
The development set contains 210 tweets of Tweebank V1 Dev and another 500 tweets in feb\_jul\_16 corpus.
The test set contains all the 201 tweets in the test set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.

@@

% tweets, tokens, tokens/tweet, part/tweet, token types.
\begin{table}[t]
\centering
 \begin{tabular}{l r r r} 
 \hline
 			& 	Train 		& 	Dev		&	Test\\[0.5ex] \hline
tweets 		&	1639 		&	709		&	1201\\
tokens 		&			&			&	\\
types 		&	 		&			&	\\
parts		 	&	 		&			&	\\ \hline
\end{tabular}
 \caption{Basic Statistics of Tweebank}
 \label{tab1}
\end{table}

% tokens and its proportions for the previous language phenomena.
\subsubsection{Twitter Specific Statistics}\label{lingphen}
Following the discussion of the Twitter specific linguistic phenomena, we obtain Table~\ref{tab2}.

\begin{table*}[t]
\centering
\small
 \begin{tabular}{r | l | l | l | r r r r r} 
 \hline
\multicolumn{4}{l}{}	&	Train		&	Test	&	Dev	&	All	&	Per\\[0.5ex] \hline\hline
\multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
			 	&	  		&		&		&		&		\\
\cline{2-9}
						&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
			 	&	  		&		&		&		&		\\
						&								&									&	non-syntactic
				&	  		&		&		&		&		\\
\cline{3-9}
						&								&	\multirow{2}{*}{hashtag}				&	syntactic
				&	  		&		&		&		&		\\
						&								&									&	non-syntactic
				&	  		&		&		&		&		\\
\cline{3-9}
						&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
				&	  		&		&		&		&		\\
						&								&									&	non-syntactic
				&	  		&		&		&		&		\\
\cline{3-9}
						&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
				&	  		&		&		&		&		\\
						&								&									&	non-syntactic
				&	  		&		&		&		&		\\
\cline{2-9}
						&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
				&	  		&		&		&		&		\\

\hline
\multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
			 	&	  		&		&		&		&		\\
						&	\multicolumn{3}{l |}{at-mentioned}
				&	  		&		&		&		&		\\
						&	\multicolumn{3}{l |}{parataxis without punctuations}
				&	  		&		&		&		&		\\
\hline
\end{tabular}
 \caption{Twitter Specific Statistics of Tweebank}
 \label{tab1}
\end{table*}
%annotation statistics, agreement
